### 2024-08-20 paper.tex
started trying to prove alternative characterization of set of bs. found that original definition of set of bs is horrible and unworkable.

\subsection{The centralizer of a nilpotent matrix}
\begin{definition}
    A matrix \(Y\) is \emph{Toeplitz} if it is constant along bands parallel to the main diagonal.
    That is, \(\forall i,j,k. \; Y_{ij} = Y_{i + k, j + k}\).
\end{definition}
\begin{definition}
    An \(m \times n\) matrix \(Y\) is \emph{lower-left Toeplitz} if it is Toeplitz and, in addition, we have \(y_{n - i, j - 1} = 0\) whenever \(i + j \geq \min(m,n)\).
\end{definition}
That is, \(Y\) is lower-left Toeplitz if it is Toeplitz, and the only nonzero entries are those with Manhattan distance less than \(\min(m,n)\) from the lower-left corner.
In yet other words, all but the leftmost (equivalently, bottommost) \(\min(m,n)\) diagonal bands are zero.

@@

\begin{theorem}\label{normalization}
    For any finite-dimensional \(V\), nilpotent \(A : V \to V\), and linear \(f : V \to \mathbb{C}\), there is a Jordan basis \(e_{ij}\) for \(A\) such that there is at most one pair \((i, j)\) with \(f(e_{ij}) \neq 0\).
\end{theorem}
\begin{proof}
    \cref{normalization_helper_one} gives us a Jordan basis \(e_{ij}\) such that for all \(i \neq i_0\) and all \(j\), we have \(f(e_{ij}) = 0\).
    Restricting \(A\) to \(\langle e_{i_0j}\rangle_{j \textrm{ arbitrary}}\) gives a Jordan block, and then applying \cref{normalization_helper_two} gives the desired result.
\end{proof}

@@

\begin{lemma}\label{alternative_bs}
    Here we have an alternative characterization of \(B_{I, (\rho_i)}\).
    Namely,
    \[B_{I, (\rho_i)} = \{b \in \mathbb{C}^m : \forall i \in I. \; p_i = \rho_i \land \forall i \notin I. \; p_i = \min(p_{i_k}, \lambda_i - q_{i_k}), \]
    \[\textrm{ where } k = ...\}\]
\end{lemma}
\begin{proof}
    TODO
\end{proof}

\subsection{Irreducible components of \(U_{I, (\rho_i)}\)}

@@

Let \(\mu\) be the shape of the Jordan basis given in the previous lemma.
Let \(X_\mu\) be the Springer fiber at \(J(\mu)\).

\begin{lemma}
    \(U_{I, (\rho_i)} \cong B_{I, (\rho_i)} \times X_\mu\).
\end{lemma}
\begin{proof}
    For \(b \in B_{I, (\rho_i)}\), let \(P_b\) be the change-of-basis matrix, with columns given by the Jordan basis of the previous lemma, so that \(J(\mu) = P_b^{-1} A_{0,b} P_b\).
    From looking at the Jordan basis of the previous lemma (the basis can be expressed in terms of \(A, \lambda, e_{ij}, f_i, I, \rho_i, b\)), it is clear that the map \(P : B_{I, (\rho_i)} \to \GL_{m + n}\), given by \(b \mapsto P_b\), is algebraic.
    \par Now, we remark that the Springer fiber at \(A_{0,b}\) is simply \(\{P_b U : U \in X_\mu\}\).
    This gives us the isomorphism \(B_{I, (\rho_i)} \times X_\mu \to U_{I, (\rho_i)}\).
    \[(b, U) \mapsto (P_b J(\mu) P_b^{-1}, P_b U),\]
    with inverse
    \[(A_{0,b}, U) \mapsto (b, P_b^{-1} U).\]
\end{proof}
At last we have reached the base of our recursive procedure, and we begin to propagate upwards.
We write \((X_{\mu, \alpha})_\alpha\) to denote the irreducible components of \(X_\mu\).
\begin{lemma}
    The irreducible components of \(U_{I, (\rho_i)}\) are exactly the subvarieties 
    \[U_{I, (\rho_i), \alpha} := \{(P_b J(\mu) P_b^{-1}, P_b U) : b \in B_{I, (\rho_i)}, U \in X_{\mu, \alpha}\}.\]
    These are distinct.  
    There are blah of them, and each has dimension blah.
\end{lemma}
\begin{proof}
    We know from \cref{bs_iso} that \(B_{I, (\rho_i)}\) is irreducible.
    So, the components of \(B_{I, (\rho_i)} \times X_\mu\) are obviously \(B_{I, (\rho_i)} \times X_{\mu, \alpha}\).
    Their dimensions are blah, and there are... of them.
    taking image under the isomorphism gives the desired result.
\end{proof}

\subsection{Conclusion}
\begin{lemma}
    The irreducible components of \(U_0\) are exactly the \(U_{I, (\rho_i), \alpha}\).
    They are distinct.
    There are blah of them, each of dimension blah.
\end{lemma}

>>>>

\subsection{The centralizer of a nilpotent matrix}
\begin{definition}
    A matrix \(Y\) is \emph{Toeplitz} if it is constant along bands parallel to the main diagonal.
    That is, \(\forall i,j,k. \; Y_{ij} = Y_{i + k, j + k}\).
\end{definition}
\begin{definition}
    An \(m \times n\) matrix \(Y\) is \emph{lower-left Toeplitz} if it is Toeplitz and, in addition, we have \(y_{n - i, j - 1} = 0\) whenever \(i + j \geq \min(m,n)\).
\end{definition}
That is, \(Y\) is lower-left Toeplitz if it is Toeplitz, and the only nonzero entries are those with Manhattan distance less than \(\min(m,n)\) from the entry in the bottom-left corner.
In yet other words, all but the leftmost (equivalently, bottommost) \(\min(m,n)\) diagonal bands are zero.

@@

\begin{theorem}\label{normalization}
    For any finite-dimensional \(V\), nilpotent \(A : V \to V\), and linear \(f : V \to \mathbb{C}\), there is a Jordan basis \(e_{ij}\) for \(A\) such that there is at most one pair \((i, j)\) with \(f(e_{ij}) \neq 0\).
\end{theorem}
\begin{proof}
    \cref{normalization_helper_one} provides a Jordan basis \(e_{ij}\) such that for all \(i \neq i_0\) and all \(j\), we have \(f(e_{ij}) = 0\).
    Restricting \(A\) to \(\langle e_{i_0j}\rangle_{j \textrm{ arbitrary}}\) gives a Jordan block, and then applying \cref{normalization_helper_two} gives the desired result.
\end{proof}

@@

\subsection{A study of \(U_{I, (\rho_i)}\)}

@@

Let \(\mu(I, (\rho_i))\) be the shape of the Jordan basis given in the previous lemma.
Let \(X_\mu\) be the Springer fiber at \(J(\mu)\).

\begin{lemma}
    \(U_{I, (\rho_i)} \cong B_{I, (\rho_i)} \times X_\mu\).
\end{lemma}
\begin{proof}
    For \(b \in B_{I, (\rho_i)}\), let \(P_b\) be the change-of-basis matrix, with columns given by the Jordan basis of the previous lemma, so that \(J(\mu) = P_b^{-1} A_{0,b} P_b\).
    From looking at the Jordan basis of the previous lemma (the basis can be expressed in terms of \(A, \lambda, e_{ij}, f_i, I, \rho_i, b\)), it is clear that the map \(P : B_{I, (\rho_i)} \to \GL_{m + n}\), given by \(b \mapsto P_b\), is algebraic.
    \par Now, we remark that the Springer fiber at \(A_{0,b}\) is simply \(\{P_b U : U \in X_\mu\}\).
    This gives us the isomorphism \(B_{I, (\rho_i)} \times X_\mu \to U_{I, (\rho_i)}\).
    \[(b, U) \mapsto (P_b J(\mu) P_b^{-1}, P_b U),\]
    with inverse
    \[(A_{0,b}, U) \mapsto (b, P_b^{-1} U).\]
\end{proof}

\subsection{A study of \(B_{I, (\rho_i)}\)}
Fix any \(I\) and \((\rho_i)\) satisfying the conditions of \cref{bs_union}.
Define \(\{i_1 < \cdots < i_r\} := I\).
For notational convenience (although we assign meaning to neither \(i_0\) nor \(i_{r + 1}\)), we define \(q_{i_0} := n\), and \(p_{i_{r + 1}} := 0\).
To see why this choice makes some sort of sense, look at the shape \(\mu\) of the Jordan basis of the previous subsection.
Note that for any \(b \in B_{I, (\rho_i)}\) we have \(p_{i_1} > \cdots > p_{i_r} > p_{i_{r + 1}}\), and also \(q_{i_0} > q_{i_1} > \cdots > q_{i_r}\).
\par First, we provide an alternative characterization of \(B_{I, (\rho_i)}\).
\begin{lemma}\label{alternative_bs}
    \(B_{I, (\rho_i)} = B_{I, (\rho_i)}'\), where
    \[B_{I, (\rho_i)}' := \{b \in \mathbb{C}^m : \forall i \in I. \; p_i \leq \rho_i \land \forall i \notin I. \; p_i = \min(p_{i_k}, \lambda_i - q_{i_k}), \]
    \[\textrm{ where } k = \min\{k \in \{1, ..., r\} : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\}.\]
\end{lemma}
\begin{proof}
    First we show that \(B_{I, (\rho_i)} \subseteq B_{I, (\rho_i)}'\).
    Let \(b \in B_{I, (\rho_i)}\).
    It is clear that \(\forall i \in I. \; p_i = \rho_i\).
    So, let \(i \notin I\), and let \(k = \min\{k : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
    We need to show that \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\).

\subsection{Conclusion}
At last we have reached the base of our recursive procedure, and we begin to propagate upwards.
We write \((X_{\mu, \alpha})_\alpha\) to denote the irreducible components of \(X_\mu\).
\begin{lemma}
    The irreducible components of \(U_{I, (\rho_i)}\) are exactly the subvarieties 
    \[U_{I, (\rho_i), \alpha} := \{(P_b J(\mu) P_b^{-1}, P_b U) : b \in B_{I, (\rho_i)}, U \in X_{\mu, \alpha}\}.\]
    These are distinct.  
    There are blah of them, and each has dimension blah.
\end{lemma}
\begin{proof}
    We know from \cref{bs_iso} that \(B_{I, (\rho_i)}\) is irreducible.
    So, the components of \(B_{I, (\rho_i)} \times X_\mu\) are obviously \(B_{I, (\rho_i)} \times X_{\mu, \alpha}\).
    Their dimensions are blah, and there are... of them.
    taking image under the isomorphism gives the desired result.
\end{proof}

\begin{lemma}
    The irreducible components of \(U_0\) are exactly the \(U_{I, (\rho_i), \alpha}\).
    They are distinct.
    There are blah of them, each of dimension blah.
\end{lemma}
